%-------------------------
% Yash Mittal - One Page Resume (With Profile Links)
%-------------------------
\documentclass[9.5pt,letterpaper]{article}

\usepackage[left=0.25in, right=0.25in, top=0.25in, bottom=0.25in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{array}
\usepackage{tabularx}

\hypersetup{colorlinks=true, urlcolor=blue}
\pagestyle{empty}
\raggedbottom
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}

% Section formatting
\titleformat{\section}
  {\vspace{-4pt}\bfseries\large}
  {}{0em}{}[\vspace{1pt}\titlerule\vspace{-2pt}]
\titlespacing*{\section}{0pt}{5pt}{4pt}

%---- Custom Commands ----
\newcommand{\resumeItem}[1]{%
  \item\small{#1\vspace{-1pt}}%
}

\usepackage{titlesec}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0em}
  {}
  [\vspace{-0.2ex}\titlerule]

\titlespacing*{\section}
  {0pt}
  {0.4ex}
  {0.5ex}

\newenvironment{resumeList}{%
  \begin{itemize}[
    leftmargin=0.18in,
    label=\textbullet,
    itemsep=1pt,
    topsep=3pt,
    parsep=0pt
  ]%
}{%
  \end{itemize}\vspace{-2pt}%
}

\newenvironment{outerList}{%
  \begin{itemize}[leftmargin=0pt, label={}, itemsep=0pt, topsep=0pt, parsep=0pt]%
}{%
  \end{itemize}%
}

\newcommand{\workEntry}[3]{%
  \item[]
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} \textit{\small $|$ #2} & \small #3
  \end{tabularx}\vspace{1pt}
}

\newcommand{\projectEntry}[2]{%
  \item[]
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} & \small\textit{#2}
  \end{tabularx}\vspace{1pt}
}

\newcommand{\eduEntry}[3]{%
  \item[]
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} \textit{\small $|$ #2} & \small #3
  \end{tabularx}\vspace{1pt}
}

%==========================================
\begin{document}
%==========================================

%---------- HEADER ----------
\begin{center}
  {\LARGE\bfseries YASH MITTAL}\\[4pt]
  \small
  % ---- ROW 1: Contact Info ----
  \faPhone~+91-9457016627\enspace\textbar\enspace
  \faEnvelope~\href{mailto:mittalyash616@gmail.com}{mittalyash616@gmail.com}\enspace\textbar\enspace
  \faLinkedin~\href{https://linkedin.com/in/yash-mittal-a42645319}{linkedin.com/in/yash-mittal-a42645319}\\[3pt]
  % ---- ROW 2: Profile Links ----
  \faGithub~\href{https://github.com/mittalyash616}{github.com/mittalyash616}\enspace\textbar\enspace
  \faCode~\href{https://codolio.com/profile/yash_mittal}{codolio.com/profile/yash\_mittal}
\end{center}
\vspace{-8pt}

%---------- PROFESSIONAL SUMMARY ----------
\section{Professional Summary}

\small
Computer Science Engineering student specializing in Artificial Intelligence with a strong foundation in Cloud Computing and Competitive Programming. Experienced in building AI-powered applications, autonomous reasoning systems and scalable backend architectures. Skilled in applying LLMOps and MLOps practices to develop, deploy and optimize production-grade machine learning solutions. Strong focus on clean architecture, performance optimization and reliability with a proven ability to translate complex problems into efficient, real-world software systems.

%---------- TECHNICAL SKILLS ----------
\vspace{2pt}
\section{Technical Skills}
\small
\begin{tabularx}{\linewidth}{@{} >{\bfseries}l X @{}}
  Languages:           & C++, Java, Python, HTML5, CSS3, JavaScript, SQL \\
  Frameworks:          & FastAPI, Flask, LangChain, Streamlit  \\
  AI \& Cloud:         & Machine Learning, LLMOps, MLOps, RAG, Multimodal AI, PyTorch, Scikit-learn \\
  Platforms:     & AWS, Vercel, Hugging Face, Kaggle, GitHub, Docker \\
  Core Skills:   & Data Structures \& Algorithms, Competitive Programming, Problem Solving, Project Management \\
\end{tabularx}

%---------- CERTIFICATIONS ----------
\vspace{2pt}
\section{Certificates}
\begin{resumeList}
  \resumeItem{AWS Certified AI Practitioner (AIF-C01) - AWS}
  \resumeItem{Machine Learning Specialisation — Coursera}
  \resumeItem{Software Engineering — NPTEL }
\end{resumeList}

%---------- WORK EXPERIENCE ----------
\vspace{2pt}
\section{Work Experience}
\begin{outerList}
    
  \workEntry{AI Intern}{Infosys Springboard, Remote}{Feb. 2026 – Apr. 2026}
  \vspace{-15pt}
  \begin{resumeList}
    \resumeItem{Developing \textbf{ClinScan Lung-Abnormality Detection} on Chest X-rays using deep learning and computer vision techniques.}
    \resumeItem{Designing and implementing AI-powered diagnostic pipelines in collaboration with cross-functional engineering teams.}
  \end{resumeList}
\vspace{5pt}
  \workEntry{Senior Executive – Placement Turnaround}{Dean Career Cloud | SCSET, Greater Noida}{Feb. 2026 – Present}
  \vspace{-15pt}
  \begin{resumeList}
    \resumeItem{Driving placement initiatives and career development programs to improve student employment outcomes at scale.}
    \resumeItem{Coordinating with industry partners to establish internship opportunities and full-time job pipelines for students.}
  \end{resumeList}
\vspace{5pt}
  \workEntry{Placement Coordinator}{Bennett University, Greater Noida}{Jan. 2026 – Present}
  \vspace{-15pt}
  \begin{resumeList}
    \resumeItem{Managed and maintained student databases to efficiently track placements and employer interactions.}
    \resumeItem{Built relationships with industry partners to identify and secure internship and job openings for students.}
  \end{resumeList}
\vspace{5pt}
  \workEntry{Data Science Intern}{Finlatics}{Dec. 2024 – Feb. 2025}
  \begin{resumeList}
    \vspace{-5pt}
    \resumeItem{Analyzed real-world company datasets using Python to uncover patterns, trends, and insights for informed decision-making.}
    \resumeItem{Applied data wrangling, exploratory data analysis, and visualization techniques to deliver business intelligence reports.}
  \end{resumeList}

\end{outerList}

%---------- PROJECTS ----------
\vspace{2pt}
\section{Projects}
\begin{outerList}

  \projectEntry{AgroVision — Multimodal AI Agent for Agriculture}{\href{https://agro-vision-frontend.vercel.app}{agro-vision-frontend.vercel.app}}
  \vspace{-15pt}
  \begin{resumeList}
    \resumeItem{Developed an AI-powered Smart Crop Advisory System enabling crop selection, pest and disease detection, and soil health insights for small and marginal farmers.}
    \resumeItem{Built and deployed machine learning models for crop recommendation, market price prediction, and weather forecasting, and implemented YOLO-based computer vision for pest and disease detection.}
    \resumeItem{Tools: Python, YOLO, OpenCV, Scikit-learn, XGBoost, TensorFlow, FastAPI, Firebase, Pandas, NumPy, LangChain}
  \end{resumeList}
\vspace{5pt}
  \projectEntry{Real-Time Medical Assistant}{}
  \vspace{-15pt}
  \begin{resumeList}
    \resumeItem{Developed an AI-driven Agri-Tech platform enabling data-driven farming through crop recommendation, soil health analysis, and real-time advisory.}
    \resumeItem{Implemented computer vision-based pest and disease detection using deep learning models to provide precise treatment recommendations.}
    \resumeItem{Built predictive models for market price forecasting and weather-based planning to optimize farmer profitability and decision-making.}
    \resumeItem{Tools: Python, YOLO, OpenCV, Scikit-learn, XGBoost, TensorFlow, FastAPI, Firebase, Pandas, NumPy.}
  \end{resumeList}
\vspace{5pt}
  \projectEntry{AI-Based End-to-End Career Preparation Platform}{\href{https://placemate-ai-two.vercel.app}{placemate-ai-two.vercel.app}}
  \vspace{-15pt}
  \begin{resumeList}
    \resumeItem{Built an AI-powered platform integrating LinkedIn, GitHub, and Codlio to generate ATS-optimized resumes with real-time keyword analysis and scoring.}
    \resumeItem{Developed a closed-loop system including resume-based mock interviews, behavioural \& DSA interview prep and company-wise coding patterns for complete placement preparation.}
    \resumeItem{Tools: Python, Firebase, Docker, Hugging Face, Vercel, LLM APIs, NLP, Speech-to-Text, Text-to-Speech}
  \end{resumeList}

\end{outerList}

%---------- EDUCATION ----------
\vspace{2pt}
\section{Education}
\begin{outerList}

  \eduEntry{B.Tech Computer Science \& Engineering (AI/ML)}{Bennett University,Greater Noida,Uttar Pradesh,India}{2024 - 2028}
  \vspace{-15pt}
  \begin{resumeList}
    \resumeItem{CGPA: \textbf{10.0 CGPA} (Till 3rd Semester)}
  \end{resumeList}
\vspace{5pt}
  \eduEntry{Intermediate (Class XII)}{M.G. Public School,Muzaffarnagar,Uttar Pradesh,India}{2022 - 2024}
  \vspace{-15pt}
  \begin{resumeList}
    \resumeItem{Scored \textbf{92.4\%} — Ranked 4\textsuperscript{th} in school}
  \end{resumeList}
\vspace{5pt}
  \eduEntry{High School (Class X)}{M.G. Public School,Muzaffarnagar,Uttar Pradesh,India}{2010 - 2022}
  \vspace{-15pt}
  \begin{resumeList}
    \resumeItem{Scored \textbf{96.6\%} — Ranked 5\textsuperscript{th} in school}
  \end{resumeList}

\end{outerList}

\end{document}